---
title: "Recruitment Overview"
author: "Luran Manfio"
date: "1/15/2020"
output:
  html_document:
    highlight: tango
    theme: spacelab
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---


```{r, include=FALSE, warning=FALSE}

library(tidyr)
library(dplyr)
library(ggplot2)
library(keyringr)
library(redcapAPI)
library(REDCapR)
library(lubridate)
library(formattable)
library(broom)

# **************************************************************************** #
# ***************  Pull data from redcap with api                                              
# **************************************************************************** # 

# Get Redcap API Token
# # https://cran.r-project.org/web/packages/keyringr/vignettes/Avoiding_plain_text_passwords_in_R_with_keyringr.html
credential_label <- "interview_api"
credential_path <- paste(Sys.getenv("USERPROFILE"), '\\DPAPI\\passwords\\', Sys.info()["nodename"], '\\', credential_label, '.txt', sep="")
uri <- "https://redcap.ctsi.ufl.edu/redcap/api/"
beach_token<-decrypt_dpapi_pw(credential_path)
print(beach_token)

# Create connections
rcon <- redcapConnection(url=uri, token=beach_token)


# crc variables

desired_fields <- c("record_id","int_phone_pass_fail","encounter_date_int","encounter_type_int",
"beach_interview_study_encounters_complete",
"learn_about_study_int","int_consent_complete",
"analysis_mat_age_cats","analysis_bmi","mom3t_education_2",
"analysis_mat_age","analysis_income","analysis_kids_previous")


# events to retain

events_to_retain  <- c("beach_interview_phone_screen","beach_interview_study_encounters")

# list of events

# list records
#exportRecords(rcon)  I don't know why having this in a report is an issue

# export field names

# consented records
records.v1=c("BIS001A","BIS002A","BIS003A","BIS004A","BIS005A",
                     "BIS006A","BIS007A","BIS008A","BIS009A","BIS010A",
                     "BIS011A","BIS013A","BIS014A","BIS018A","BIS019A",
                     "BIS022A","BIS023A","BIS024A","BIS025A","BIS026A",
                     "BIS027A","BIS028A","BIS029A","BIS030A","BIS031A",
                     "BIS032A","BIS033A","BIS034A",
                     "PRG001","PRG002","PRG003","PRG004","PRG005",
                     "PRG006","PRG007","PRG008","PRG009","PRG010",
                     "PRG011","PRG012","PRG013","PRG014","PRG015",
                     "PRG016","PRG017","PRG018","PRG020",
                     "156","157","195","196","214","216","224","225","228",
                     "230","234","235","238","239",
                     "240","241","242","245","246","251","255","257","258",
                     "259","260","261","262","265","266","267",
                     "268","269","270","271","273","274","275","276","277",
                     "278","280","281","282","283","286","289",
                     "290","291","293","294","295","296","297","85","88","90")

ds <- data.frame(records.v1)

# pull data
ds_some_rows_v1 <- redcap_read(
  redcap_uri = uri, 
  records= records.v1,
  token      = beach_token, 
  fields     = desired_fields
  
)$data
```

```{r echo=FALSE, warning=FALSE}
# recode encounter type
ds_some_rows_v1=ds_some_rows_v1 %>%
  #use mutate(new column = recode(current column to be recoded, "variable in column"="new variable name"))
    mutate(learn_about_study = recode(learn_about_study_int, "1"="Flyer","3"="Facebook","5"="Other"))%>%
  replace_na(list( learn_about_study = "Didn't Respond"))%>%
  mutate(education_level = recode(mom3t_education_2,"1"="8th grade or less","2"="some high school","3"="high school diploma/GED","4"="some college or community college","5"="Associates degree","6"="completed tech or vocational school","7"="college graduate","8"="some graduate or professional school","9"="Graduate or professional degree"))%>%
  mutate(previous_kids = recode(analysis_kids_previous, "1"="yes","0"="no"))%>%
  mutate(income = recode(analysis_income, "1"="$0-$15,000","2"="$15,001-$19,000","3"="$19,001-$37,000","4"="$37,001-$44,000","5"="$44,001-$52,000","6"="$52,001-$56,000","7"="$56,001-$67,000","8"="$67,001-$79,000","9"="$79,001 or more"))%>%
  mutate(phone_pass_fail = recode(int_phone_pass_fail, "1"="pass","0"="fail"))%>%
  mutate(consent_complete = recode(int_consent_complete, "1"="Consented","0"="not Consented","NA"="Did not respond"))

```
# Recruitment overview

##### One of the major reasons for research delay has been recruitment issues. 9 out of 10 trials require the original timeline to be extended due to lack of participants. The problem with recruitment stems from a lack of innovation within the field and use of out of date practices. However, new methods have arisen that can prove to be a solution to the issues with current recruitment methods. The use of Facebook for recruitment solves the problems of participant targeting and recruitment rates. Within the BEACH Interview study, we recruited both through flyers and Facebook; however, to truly test the effectiveness of the Facebook method against the traditional method of flyers, we only conducted an ad for discrete periods of time. Following the study's completion, we analyzed our recruitment and found statistically significant differences between our two groups: pregnant and breastfeeding moms.

#### The Objectives of this study are to:
#### 1.) Preform exploratory data analysis to discover statistically significant difference between traditional and modern recruitment methods.
#### 2.) preform similar analysis on the BEACH study to prove support the analysis found in this study.
#### 3.) Confirm analysis on the BEACH study to prove support the analysis found in this study.

#### Below we have the numbers of participants we recruited per quarter broken down by how they heard of our study. We show both screened and consented participants over the course of the study.

## Participants screened
```{r, echo=FALSE, warning=FALSE}
Encounter_per_time <- ds_some_rows_v1%>%
  select(encounter_date_int,learn_about_study)

Encounter_per_time$encounter_date_int <- as.Date(Encounter_per_time$encounter_date_int, format= "%Y-%m-%d")

my_data <- data.frame(encounter_date_int = seq(as.Date("2017-01-01"), as.Date("2019-12-31"), 
  by = "1 month"), format= "%Y-%m-%d")

my_complete <- full_join(my_data, Encounter_per_time, by = "encounter_date_int")

Encounter_per_time <- my_complete%>%
  separate(encounter_date_int,c("y","m","d"))%>%
  mutate(Quarter = case_when(
    m == "01" | m == "02" | m == "03" ~ "Q1",
    m == "04" | m == "05" | m == "06" ~ "Q2",
    m == "07" | m == "08" | m == "09" ~ "Q3",
    m == "10" | m == "11" | m == "12" ~ "Q4",
    TRUE~"Q5"))%>%
  group_by(learn_about_study,y,Quarter)%>%
  summarize(count=n())%>%
  unite("YQ",c("y",Quarter),sep ="-")


theme_set(theme_classic())
# distribution of visits each month(histogram)
h <- ggplot(Encounter_per_time, aes(YQ, count)) + scale_fill_brewer(palette = "Spectral")
h + geom_histogram(aes(fill=factor(learn_about_study)), stat = "Identity",
                   bins=24,
                   col="black", 
                   size=.1) + # change number of bins
  # geom_density() + #this function is meant to draw a trend line for the graph
  # stat_bin(aes(y=count,label=count),geom="text",vjust=-.5) +   # this will display the total count of each bin
  labs(title="How participants heard of our study monthly", 
       subtitle="from july of 2017-January 2019",
       x="Date(Year-Month)",
       y="Count",
       fill="How did you learn about the study") +
  theme(axis.text.x = element_text(angle=70, vjust =.6))
```

```{r echo=FALSE, warning=FALSE}
Totals <- ds_some_rows_v1%>%
  select(learn_about_study)%>%
  group_by(learn_about_study)%>%
  summarize(count=n())%>%
  rename("how did you hear about us?"=learn_about_study,"Total"=count)

formattable(Totals, align =c("l","r"))

Monthly_recruitment <- ds_some_rows_v1%>%
  select(learn_about_study,encounter_date_int)%>%
  separate(encounter_date_int,c("y","m","d"))%>%
  unite("YM",c("y","m"),sep ="-")%>%
  group_by(YM)%>%
  summarise(count=n())%>%
  rename("Recruitment for the month"=count,"Month of Recruitment"=YM)


#formattable(Monthly_recruitment, align =c("l","r"))
```

## Consented Particiapnts 
```{r, echo=FALSE, warning=FALSE, fig.cap= "Fig6: Consented Participants Over Time"}
# Provides a filter to the data to view how particpnats heard about the study AND consented. Showed greater favor for Facebook recruitment.

Encounter_per_time <- ds_some_rows_v1%>%
  select(encounter_date_int,learn_about_study, consent_complete)%>%
  filter(consent_complete=="Consented")

Encounter_per_time$encounter_date_int <- as.Date(Encounter_per_time$encounter_date_int, format= "%Y-%m-%d")

my_data <- data.frame(encounter_date_int = seq(as.Date("2017-01-01"), as.Date("2019-12-31"), 
  by = "1 month"), format= "%Y-%m-%d")

my_complete <- full_join(my_data, Encounter_per_time, by = "encounter_date_int")

Encounter_per_time <- my_complete%>%
  separate(encounter_date_int,c("y","m","d"))%>%
  mutate(Quarter = case_when(
    m == "01" | m == "02" | m == "03" ~ "Q1",
    m == "04" | m == "05" | m == "06" ~ "Q2",
    m == "07" | m == "08" | m == "09" ~ "Q3",
    m == "10" | m == "11" | m == "12" ~ "Q4",
    TRUE~"Q5"))%>%
  
  group_by(learn_about_study,y,Quarter)%>%
  summarize(count=n())%>%
  unite("YQ",c("y",Quarter),sep ="-")


#Consent_per_Time <- ds_some_rows_v1%>%
#  select(encounter_date_int,learn_about_study, consent_complete)%>%
#  separate(encounter_date_int,c("y","m","d"))%>%
#  filter(consent_complete=="Consented")%>%
#  group_by(learn_about_study,m,y)%>%
#  summarize(count=n())%>%
#  unite("YM",c("y","m"),sep ="-")


theme_set(theme_classic())

# distribution of visits each month(histogram)
h <- ggplot(Encounter_per_time, aes(YQ, count)) + scale_fill_brewer(palette = "Spectral")
h + geom_histogram(aes(fill=factor(learn_about_study)), stat = "Identity",
                   bins=24,
                   col="black", 
                   size=.1) + # change number of bins
  #geom_text(aes(y=label_count,label=count), vjust=-.02) +  #doesn't work properly because cummulative sums aren't calulated 
  # geom_density() + #this function is meant to draw a trend line for the graph
  # stat_bin(aes(y=count,label=count),geom="text",vjust=-.5) +   # this will display the total count of each bin
  labs(title="How participants heard of our study monthly", 
       subtitle="from july of 2017-January 2019 and Have completed consent",
       x="Date(Year-Month)",
       y="Count",
       fill="How did you learn about the study") +
  theme(axis.text.x = element_text(angle=70, vjust =.6))

#formattable(Encounter_per_time,align=c("l","c","r"))
```


# Demographics



#### We focused our recruitment around 2 groups: Breastfeeding and Pregnant mother with BMI's that would represent both normal and overweight participants. For this reason, we hoped to recruit a wide range of mother with varying BMI. With Facebooks targeted approch to recruitment, it should provide particpants within the both groups that fall within our desired ranges. We tested the variance between recruitment methods and provided a visualization of both BMI and age in boxplots. Below is a review of that research over the whole study without specifying pregnant or breastfeeding.



```{r echo=FALSE,warning=FALSE}
  #Determining the average BMI per enocunter type.
Pre_BMI <- ds_some_rows_v1%>%
  select(record_id,analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  filter(!is.na(learn_about_study))
  


#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Pre_BMI$learn_about_study <- as.factor(Pre_BMI$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
means <- aggregate(analysis_bmi ~  learn_about_study, Pre_BMI, mean)

  
  g <- ggplot(Pre_BMI, aes(learn_about_study, analysis_bmi))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="BMI of participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="BMI")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 0.08))


#formattable(Pre_BMI,asign=c("l","c","r"))
```

#### These tables review our recruitment between BMI groups (overweight and normal weight):

```{r echo=FALSE, warning=FALSE}

normal <- ds_some_rows_v1%>%
  select(learn_about_study,consent_complete,phone_pass_fail,analysis_bmi)%>%
  filter(analysis_bmi<25,!is.na(phone_pass_fail))

over <- ds_some_rows_v1%>%
  select(learn_about_study,consent_complete,phone_pass_fail,analysis_bmi)%>%
  filter(analysis_bmi>=25,!is.na(phone_pass_fail))



normal_sum <- normal%>%
  group_by(learn_about_study)%>%
  summarize(count=n())%>%
  rename("Encounter type"=learn_about_study, "Count of normal weight particiapnts(BMI<25)"=count)

over_sum <- over%>%
  group_by(learn_about_study)%>%
  summarize(count=n())%>%
  rename("Encounter type"=learn_about_study, "Count of overweight particiapnts(BMI>25)"=count)

#formattable(normal_sum, align =c("l","r"))
formattable(over_sum, align =c("l","r"))
```

```{r echo=FALSE, warning=FALSE}

normal <- ds_some_rows_v1%>%
  select(learn_about_study,consent_complete,phone_pass_fail,analysis_bmi)%>%
  filter(analysis_bmi<25,!is.na(phone_pass_fail))

over <- ds_some_rows_v1%>%
  select(learn_about_study,consent_complete,phone_pass_fail,analysis_bmi)%>%
  filter(analysis_bmi>=25,!is.na(phone_pass_fail))



normal_sum <- normal%>%
  group_by(learn_about_study)%>%
  summarize(count=n())%>%
  rename("Encounter type"=learn_about_study, "Count of normal weight particiapnts(BMI<25)"=count)

over_sum <- over%>%
  group_by(learn_about_study)%>%
  summarize(count=n())%>%
  rename("Encounter type"=learn_about_study, "Count of overweight particiapnts(BMI>25)"=count)

formattable(normal_sum, align =c("l","r"))
#formattable(over_sum, align =c("l","r"))
```


#### Below is a tabulation of the mean, median, and variance between Facebook and flyers to test for any statistical significance. blow represents mean, median, and an F-test to test for variance.

```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_bmi)%>%
  filter(!is.na(analysis_bmi))
mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi),learn_about_study=="Facebook")%>%
  select(analysis_bmi)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi),learn_about_study=="Flyer")%>%
  select(analysis_bmi)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var_T <- var.test(face_bmi,flyer_bmi)
glance(var_T)
```




#### We preformed the same tests with the age of the participants.

```{r, echo=FALSE ,fig.cap= "Fig9: Participant Age"}
#select all the maternal ages and remove NA values:

Mat_age <- ds_some_rows_v1%>%
  select(record_id,analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  filter(!is.na(learn_about_study))
  

#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Mat_age$learn_about_study <- as.factor(Mat_age$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
  g <- ggplot(Mat_age, aes(learn_about_study, analysis_mat_age))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="Age of Participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="Age(years)")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 6))
  
#formattable(Mat_age,asign=c("l","c","r"))
```

#### Below we have the statistics of age.
```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_mat_age)%>%
  filter(!is.na(analysis_mat_age))
mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age),learn_about_study=="Facebook")%>%
  select(analysis_mat_age)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age),learn_about_study=="Flyer")%>%
  select(analysis_mat_age)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var.test(face_bmi,flyer_bmi)
```

#### Following a review of the entire study we reviewed our two groups of interest: pregnant and breastfeeding.

#### Below we analyzed our pregnant group first against their BMI's and ages to test for any statistical significance between recruitment methods.

#### we first reviewed the particiapnts BMI.

```{r echo=FALSE,warning=FALSE}
  #Determining the average BMI per enocunter type.
Pre_BMI <- ds_some_rows_v1%>%
  select(record_id,analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(26:44)%>%
  filter(!is.na(learn_about_study))
  


#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Pre_BMI$learn_about_study <- as.factor(Pre_BMI$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
means <- aggregate(analysis_bmi ~  learn_about_study, Pre_BMI, mean)

  
  g <- ggplot(Pre_BMI, aes(learn_about_study, analysis_bmi))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="BMI of pregnant participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="BMI")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 0.08))


#formattable(Pre_BMI,asign=c("l","c","r"))
```

#### We preformed statistical analysis within the group against recruitment methods and tested mean, median, and variance.
```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_bmi,record_id)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(26:44)

mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(26:44)%>%
  filter(learn_about_study=="Facebook")%>%
  select(analysis_bmi)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(26:44)%>%
  filter(learn_about_study=="Flyer")%>%
  select(analysis_bmi)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var.test(face_bmi,flyer_bmi)
```

#### We preformed the same review for our pregnant mothers' groups.

```{r, echo=FALSE ,fig.cap= "Fig9: Participant Age"}
#select all the maternal ages and remove NA values:

Mat_age <- ds_some_rows_v1%>%
  select(record_id,analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(26:44)%>%
  filter(!is.na(learn_about_study))
  

#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Mat_age$learn_about_study <- as.factor(Mat_age$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
  g <- ggplot(Mat_age, aes(learn_about_study, analysis_mat_age))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="Age of Participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="Age(years)")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 5.5))
  
#formattable(Mat_age,asign=c("l","c","r"))
```

#### We preformed statistical analysis within the group against recruitment methods and tested mean, median, and variance.
```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_mat_age,record_id)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(26:44)

mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(26:44)%>%
  filter(learn_about_study=="Facebook")%>%
  select(analysis_mat_age)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(26:44)%>%
  filter(learn_about_study=="Flyer")%>%
  select(analysis_mat_age)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var.test(face_bmi,flyer_bmi)
```

#### Below we analyzed our Breastfeeding group against their BMI's and ages to test for any statistical significance between recruitment methods.

#### we first reviewed the participants BMI.

```{r echo=FALSE,warning=FALSE}
  #Determining the average BMI per enocunter type.
Pre_BMI <- ds_some_rows_v1%>%
  select(record_id,analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(1:25)%>%
  filter(!is.na(learn_about_study))
  


#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Pre_BMI$learn_about_study <- as.factor(Pre_BMI$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
means <- aggregate(analysis_bmi ~  learn_about_study, Pre_BMI, mean)

  
  g <- ggplot(Pre_BMI, aes(learn_about_study, analysis_bmi))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="BMI of pregnant participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="BMI")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 0.08))


#formattable(Pre_BMI,asign=c("l","c","r"))
```

####We preformed statistical analysis within the group against recruitment methods and tested mean, median, and variance.
```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_bmi,record_id)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(1:25)

mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(1:25)%>%
  filter(learn_about_study=="Facebook")%>%
  select(analysis_bmi)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_bmi,learn_about_study)%>%
  filter(!is.na(analysis_bmi))%>%
  slice(1:25)%>%
  filter(learn_about_study=="Flyer")%>%
  select(analysis_bmi)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var.test(face_bmi,flyer_bmi)
```

#### We preformed the same analysis for breastfeeding mother's age. Our analysis is below.

```{r, echo=FALSE ,fig.cap= "Fig9: Participant Age"}
#select all the maternal ages and remove NA values:

Mat_age <- ds_some_rows_v1%>%
  select(record_id,analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(1:25)%>%
  filter(!is.na(learn_about_study))
  

#create a marginal Histogram / Boxplot for maternal ages by encounter type:
Mat_age$learn_about_study <- as.factor(Mat_age$learn_about_study)

    library(ggplot2)
  theme_set(theme_classic())
  
  # Plot
  g <- ggplot(Mat_age, aes(learn_about_study, analysis_mat_age))
  g + geom_boxplot(varwidth=T, fill="plum") + 
      labs(title="Age of Participants", 
           subtitle="Divided into how they heard of the study",
           caption="Source: BEACH Interview",
           x="How did you hear of our study",
           y="Age(years)")+
    geom_text(data = means, aes(label = analysis_bmi, y = analysis_bmi + 6))
  
#formattable(Mat_age,asign=c("l","c","r"))
```

#### We preformed statistical analysis within the group against recruitment methods and tested mean, median, and variance.
```{r echo=FALSE, warning=FALSE}
BMI <- ds_some_rows_v1%>%
  select(analysis_mat_age,record_id)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(1:25)

mean_bmi <- BMI[[1]]
mean(mean_bmi)
median(mean_bmi)
BMI_face <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(1:25)%>%
  filter(learn_about_study=="Facebook")%>%
  select(analysis_mat_age)
BMI_flyer <- ds_some_rows_v1%>%
  select(analysis_mat_age,learn_about_study)%>%
  filter(!is.na(analysis_mat_age))%>%
  slice(1:25)%>%
  filter(learn_about_study=="Flyer")%>%
  select(analysis_mat_age)
face_bmi <- BMI_face[[1]]
flyer_bmi <- BMI_flyer[[1]]

var.test(face_bmi,flyer_bmi)
```
